Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2020-01-21 acks.tex
Add epigraph to acks page (review carefully!)

\chapter{Acknowledgments}
Writing a PhD thesis is a significant challenge, both professionally and
personally; in a sense, it's a solitary challenge, but in fact I've had so much
help from so many, both in the research and in the personal growth that led me
here. In fact, this page was the hardest to write, because I knew my words could
not do justice to the task.

>>>>

\chapter{Acknowledgments}

\epigraph{No Man is an Island.}{\textit{John Donne}}
\bigskip

Writing a PhD thesis is a significant challenge, both professionally and
personally; in a sense, it's a solitary challenge, but in fact I've had so much
help from so many, both in the research and in the personal growth that led me
here. In fact, this page was the hardest to write, because I knew my words could
not do justice to the task.
